Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-16 aggregation/publication-example.tex
preparing for submission

Each system is illustrated as a table that shows the foreground model, cutoff flows, background dependencies and foreground emissions included in the system.  Aggregation results $\tilde{\mathbf{x}}$, $\tilde{\mathbf{a}}_d$, and $\tilde{\mathbf{b}}_f$ are also reported.  The table omits numeric data from most of the table for clarity. Instead, a black square indicates the presence of a nonzero value.  The systems are also reproduced as structured publications in the supplementary materials, formatted as Excel spreadsheets.

@@

The structured publication of the secondary aluminum model includes a total of 47 data points about 36 entities.  The $A_f$, $A_d$, and $B_f$ matrices are reported in sparse format, along with the aggregation vectors. In the publication, LCIA scores are reported for several impact indicators drawn from the Ecoinvent reference LCIA implementation.\footnote{The Ecoinvent LCIA factors are not published, but are available from the Ecoinvent Centre. The name of the file used in the current study is \texttt{LCIA implementation v3.1 2014\_08\_13.xlsx}.}    The $E$ matrix is also partially reproduced: entries are only reported if they match flows that appear in the foreground.

@@

The structured publication of the organic potato model reports the $A_f$, $A_d$, and $B_f$ matrices in full rather than sparse format to enable a more visually immediate review.  In addition, the $E$ matrix is reported in full, for all emissions found in the model, rather than only the emissions found in the foreground.  This enables the publication to be used to visually evaluate different implementations of the same impact assessment method in the context of the inventory model (Ecoinvent vs ILCD implementations of ReCiPe Midpoint marine eutrophication; see supplementary materials for details).

>>>>

Each system is illustrated as a table that shows the foreground model, cutoff flows, background dependencies and foreground emissions included in the system.  Aggregation results $\tilde{\mathbf{x}}$, $\tilde{\mathbf{a}}_d$, and $\tilde{\mathbf{b}}_f$ are also reported.  The table omits numeric data from most of the table for clarity. Instead, a black square indicates the presence of a nonzero value.  %The systems are also reproduced as structured publications in the supplementary materials, formatted as Excel spreadsheets.

@@

%The structured publication of the secondary aluminum model includes a total of 47 data points about 36 entities.  The $A_f$, $A_d$, and $B_f$ matrices are reported in sparse format, along with the aggregation vectors. In the publication, LCIA scores are reported for several impact indicators drawn from the Ecoinvent reference LCIA implementation.\footnote{The Ecoinvent LCIA factors are not published, but are available from the Ecoinvent Centre. The name of the file used in the current study is \texttt{LCIA implementation v3.1 2014\_08\_13.xlsx}.}    The $E$ matrix is also partially reproduced: entries are only reported if they match flows that appear in the foreground.

@@

%The structured publication of the organic potato model reports the $A_f$, $A_d$, and $B_f$ matrices in full rather than sparse format to enable a more visually immediate review.  In addition, the $E$ matrix is reported in full, for all emissions found in the model, rather than only the emissions found in the foreground.  This enables the publication to be used to visually evaluate different implementations of the same impact assessment method in the context of the inventory model (Ecoinvent vs ILCD implementations of ReCiPe Midpoint marine eutrophication; see supplementary materials for details).
